\documentclass[oneside]{article}%You can define the type of paper here.
%%Useful packages that I commonly use.
%\usepackage[numbers]{natbib}%Bibliography package (help at http://merkel.zoneo.net/Latex/natbib.php).
%\usepackage{url}%Package to highlight url.
\usepackage[utf8x]{inputenc} % for the ØMQ character
\usepackage{mathpazo}%Sets font to be math pazo.
\usepackage{alltt}%Allows the use of verbatim (good for printing out code).
%\usepackage{graphicx}%Used to import images.
\usepackage[hidelinks]{hyperref} %for using URL hyperlinks
\usepackage{amsmath, amssymb, amscd}%Contains the AMS expanded math symbols library.
\usepackage[explicit]{titlesec} %To remove section title in headers
%%For those who want smaller margins, you can use this:
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{fancyhdr} %%For headers/footers
\usepackage{savetrees} %%Removes white space
\pagestyle{fancy} %%For fancy headers
\usepackage{tocloft}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\usepackage{pdfpages}
\usepackage{graphicx} %for including graphics and figures
\usepackage{enumerate} %for custom enumerations
\usepackage{caption} %for captions outside of floats
\usepackage{chemarr} %for using xrightleftharpoons for chemical reactions
\usepackage{multirow} % for using a table label that is multiple rows in size

%for changing widths in columns for multiple columns:
\usepackage{lipsum}
\usepackage{flowfram}

\fancyhf{} %removes page enumeration from center middle of footer

\def\undertilde#1{\mathord{\vtop{\ialign{##\crcr
   $\hfil\displaystyle{#1}\hfil$\crcr\noalign{\kern1.5pt\nointerlineskip}
   $\hfil\tilde{}\hfil$\crcr\noalign{\kern1.5pt}}}}}

%For adjusting widths of columns in multicolumn environment:
%\onecolumntopinarea{static}{0pt}{.6\textwidth}{\textheight}{0pt}{0pt}
%\onecolumntopinarea{static}{0pt}{.3\textwidth}{\textheight}{.7\textwidth}{0pt}
%\onecolumntopinarea{static}{0pt}{.3\textwidth}{\textheight}{.4\textwidth}{0pt}


%for an approximate proportion symbol:
\def\approxprop{%
  \def\p{%
    \setbox0=\vbox{\hbox{$\propto$}}%
    \ht0=0.6ex \box0 }%
  \def\s{%
    \vbox{\hbox{$\sim$}}%
  }%
  \mathrel{\raisebox{0.7ex}{%
      \mbox{$\underset{\s}{\p}$}%
    }}%
}

\begin{document} 
\onecolumn

%Header / Footer information:
\fancyhead[L]{\Huge{Blair Gemmer} \small{\{\href{http://blairgemmer.com/}{blairgemmer.com} --  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -- \href{tel:4062534962}{406.253.4962}\}} \hfill \copyright \ \the\year} %%Header
\fancyfoot[L]{\small{\{\href{http://blairgemmer.com/}{blairgemmer.com} --  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -- \href{tel:4062534962}{406.253.4962}\}} \hfill v2019.07.22} %Footer

\renewcommand{\footrulewidth}{1pt}

%\twocolumn

\noindent
\huge{Experience}
%\normalsize
\small
\begin{enumerate}[]
	\item \textit{Freelance Software Engineer} \hfill May 2009 - Present\\
		\textbf{\{Missoula, Montana\}}
		\begin{enumerate}[*]
			\item Working on personal projects.
			\item Building bots for Slack and Discord.
			\item Developing and maintaining web applications for local businesses.
		\end{enumerate}
	\item \textit{CTO} \textbf{\href{https://tomis.tech}{TOMIS, LLC.}} \hfill September 2016 - July 2019\\
		\textbf{\{Missoula, Montana\}}
		\begin{enumerate}[]
			\item \textbf{Technical Lead:}
				\begin{enumerate}[-]
					\item Owning the product design from the executive vision stage to the technical implementation.
					\item Driving design and development of technical specifications.
					\item Creating realistic expectations and strategies to accomplish short and long-term goals.
					\item Research and development on the latest technology.
					\item Building prototypes and proof-of-concept on new technology.
					\item Leading back-end team in design, development, and quality assurance of REST API in Python/Django.
					\item Quality assurance and assisting in design decisions on front-end React.js application.
				\end{enumerate}
			\item \textbf{Project Management:}
				\begin{enumerate}[-]
					\item Scrum master: all Jira design, organization, and management.
					\item Typical Agile environment with daily standups and weekly sprint/scrum meetings.
					\item Jira issue board design, creation, curation, and triaging.
					\item Repository management in Bitbucket.
					\item Team communication and integration automation using Slack.
					\item Confluence documentation planning, organization, and development.
					\item Using Jira NextGen Kanban project with product roadmap feature to prioritize epics.
					\item Using Confluence's Jira templates to write release notes from Jira releases.
				\end{enumerate}
			\item \textbf{DevOps Management:}
				\begin{enumerate}[-]
					\item Managing software development lifecycle and API lifecycle.
					\item Developed rules to manage commit quality, such as requiring ticket numbers with all commits.
					\item Developed rigorous code review process with branch management rules in place for approval of pull requests.
					\item Using feature and release branches to manage healthy feature releases and hotfixes.
					\item Utilizing Bitbucket build pipelines to manage automated testing of feature branches.
					\item Using Jira and GIT to manage release tagging.
					\item Customer feedback and visual bug tracking through Usersnap.
				\end{enumerate}
			\item \textbf{Site-Reliability Engineering:}
				\begin{enumerate}[-]
					\item Application performance monitoring using DataDog and Honeycomb.
					\item Logging, host statistics, infrastructure monitoring, and incident detection using Stackdriver and DataDog.
					\item Exception reporting and ticket creation using Sentry with Jira integration.
					\item Uptime monitoring and alerting using UptimeRobot and Stackdriver.
					\item Incident handling, statuses, and post-mortems through Statuspage.io.
				\end{enumerate}
		\end{enumerate}
	\item \textit{Co-Founder, CTO} \textbf{\href{https://dotmos.com}{dotmos, LLC.}} \hfill July 2015 - January 2017\\
		\textbf{\{Missoula, Montana\}}
		\begin{enumerate}[*]
			\item \textbf{Technical Lead:} driving design and development of technical specifications for key features and tools.
			\item \textbf{Lead Software Engineer:} front-end and back-end design and development. Used Django, Node.js, and React.js.
			\item \textbf{Project Management:} development team leader, repository management, issue curation, documentation generation, team communications, and data analysis. Used BitBucket/GIT, Asana, DeployBot, Intercom, Usersnap, Open Analytics, and Slack.
		\end{enumerate}
\newpage
	\item \textit{Data Scientist, Software Engineer, etc.} \textbf{\href{https://upstreamresearch.com}{Upstream Research, Inc.}} \hfill November 2015 - September 2016\\
		\textbf{\{Missoula, Montana\}}
		\begin{enumerate}[*]
			\item \textbf{Data Scientist:} acquisition and analysis of large geographic-based data sets and creating and updating services in ArcGIS.
			\item \textbf{Software Engineer:} writing and testing automation scripts in Python and ArcPy; developing ASP.NET application using the MVC framework in C\#; designing and implementing unique solutions to novel problems; and writing and supporting custom functions in PostgreSQL.
			\item \textbf{Quality Assurance:} user-testing, writing reports, writing custom scripts in Python to test REST API endpoints, and load-testing pages and REST API endpoints.
			\item \textbf{System Administration:} deploying software releases, ensuring server up-time complied with SLA, security updates and patches, and managing Azure resources. Used Azure and Visual Studio.
			\item \textbf{Customer Support:} interfacing directly with customers and debugging customer and software issues. Used Freshdesk.
		\end{enumerate}
	\item \textit{Security Consultant} \textbf{\href{https://lmgsecurity.com/}{Lake Missoula Group, LLC.}} \hfill February 2015 - May 2015\\
		\textbf{\{Missoula, Montana\}}
		\begin{enumerate}[*]
			\item Handled a diverse client base including banks, hospitals, and retail outlets.
			\item Conducted a variety of engagements including:
				\begin{enumerate}[.]
					\item Internal and External Vulnerability Assessments (IVA, EVA).
					\item Internal and External Penetration Tests (EPT, IPT).					
					\item Web and mobile Application Security Assessments (WASA).
					\item Wireless Infrastructure Assessments (WIA).
				\end{enumerate}
			\item Wrote detailed reports and presented results for each type of engagement.
			\item Performed tech reviews on assessments conducted by other consultants.
		\end{enumerate}
	\item \textit{Senior Software Developer} \textbf{Hanna-James Enterprises, LLC.} \hfill July 2014-February 2015\\
		\textbf{\{Missoula, Montana\}}
		\begin{enumerate}[*]
			\item Developed Terminal-Based Test Automation Software in Python.
			\item Designed GUI-Based Test Automation Software in Python using GTK and wrote specification documentation in \LaTeX.
			\item Developed proof-of-concept prototype for D3-based ToR Network Tracking software in Coffeescript.
			\item Wrote specification document for GUI-Based SDK Architecture in \LaTeX.
			\item Designed and implemented entire MySQL database for SDK toolkit and implemented a data abstraction layer in Python with distinct connectors for loading the GUI, expanding a specified tool, building a tool for insertion into the database, and setting up the toolchain for execution.
		\end{enumerate}
\end{enumerate}
\
\noindent
\huge{Teaching}
\small
\begin{enumerate}[]
	\item \textit{Teacher's Assistant} \textbf{Programming Languages} \hfill Spring 2012\\
		\textit{Teacher's Assistant} \textbf{Computer Ethics} \hfill Fall 2011\\
		\textit{Instructor} \textbf{Computer Modeling} \hfill Fall 2010 - Spring 2011\\
		\textbf{\{University of Montana-Missoula\}}
		\begin{enumerate}[*]
			\item Taught freshman and sophomore students advanced features of Microsoft Excel and Access and assisted them during labs.
			\item Graded all assignments, papers, and exams. Also, maintained office hours to be available out of class for individual tutoring and fielding questions from students.
		\end{enumerate}
	\item \textit{Mentor} \textbf{The Firehose Project} \hfill Fall 2014 - Fall 2015\\
		\textbf{\href{https://thefirehoseproject.com/}{\{https://thefirehoseproject.com/\}}}
		\begin{enumerate}[*]
			\item Assisted assigned students by answering questions and working through code samples during weekly one hour online video sessions.
			\item Assisted assigned students by being available for question and code sample walkthroughs via email during regular office hours.
			\item Participated in online video group discussions surrounding larger projects.

		\end{enumerate}
\end{enumerate}
\
\noindent
\huge{Education}
%\normalsize
\small
\begin{enumerate}[]
\item \textbf{University of Montana-Missoula}\\
	\textit{M.S. Computer Science}, emphasis in \textit{Machine Learning, Data-Mining, and Simulations} \hfill May 2014
\item \textbf{University of Montana-Missoula}\\
	\textit{B.A. Psychology}, minor in \textit{Math, Media Arts} \hfill May 2010
	\
\end{enumerate}

\newpage
\noindent
\huge{Technical}
\small
\begin{enumerate}[]
	\item \textbf{Languages}
		\begin{enumerate}[*]
			 \item \textbf{Proficient:} \LaTeX, Python, Bash, JavaScript, Matlab, R, Markdown
			 \item \textbf{Familiar:} C/C++/C\#, Coffeescript, OCaml, Perl, Ruby
			 \item \textbf{Willing to Learn:} Dart, Go, Haskell
			 \item \textbf{Prefer not to use:} PHP, Java
		\end{enumerate}
	\item \textbf{Frameworks}
		\begin{enumerate}[*]
			 \item \textbf{Proficient:} Django, Django REST Framework, Flask, ASP.NET
			 \item \textbf{Familiar:} ElasticSearch, React.js, Vue.js, Node.js
		\end{enumerate}
	\item \textbf{Favorite Python Modules:} BeautifulSoup4, Celery, Matplotlib, NumPy, ØMQ, Pandas, Redis, Requests, SciPy, Scrapy, Spyder
	\item \textbf{Automation / Multitasking:} Celery, Redis, RabbitMQ, ØMQ
	\item \textbf{Machine Learning:} Keras, PyBrain, PyTorch, Scikit-Learn, TensorFlow
	\item \textbf{Data:} Access, CSV, JSON, MySQL, PostgreSQL, RESTful APIs, SQLite, SQL Server, XML, YAML
	\item \textbf{Data Visualization:} D3, Matlab, Matplotlib, R
	\item \textbf{Design:} Twitter Bootstrap, HTML5/CSS3/Sass/Less, Invision
	\item \textbf{DevOps:} Atlassian (Jira, Confluence, Statuspage, Bitbucket Pipelines), Azure, Bitbucket / GitHub (GIT), DeployBot, Docker, Google Cloud Platform, Kubernetes, Mercurial
	\item \textbf{Development Environments:} Atom, Android SDK, PyCharm, SublimeText, VIM, Visual Studio / VSCode, XCode
	\item \textbf{Development Techniques:} Agile Methodology using the Scrum or Kanban frameworks, Behavior-Driven Development, Iterative and User-Centered Design, Rapid Application Development, Test-Driven Development
	\item \textbf{Communication:} Discord, Google Hangouts, IRC, Join.me, Skype, Slack, UberConference, Zoom
	\item \textbf{APIs:} Darksky, Discord, Facebook, Google (Ads, Analytics, Maps, Places, Search Console), Instagram, Mailchimp, Pinterest, Rebrandly, Rezdy, Slack, Twilio (SMS / SendGrid), Twitter, Web CEO, Xola
	\item \textbf{Bots:} Discord, Slack
	\item \textbf{Network Security:} Aircrack-ng, Burp Suite Pro, Kali Linux, Kismet, Metasploit Framework, Nessus, NeXpose, Nmap, Wireshark/tshark
	\item \textbf{Operating Systems:} Debian and Red Hat-based Linux, Mac OS X, Windows
\end{enumerate}

\newpage
\noindent
\huge{Selected Projects}\\
\small
A list of some of my favorite personal and graduate projects, not specifically listed in my work experience, that I had the most fun on. The source code for most of the following projects is on GitHub \textbf{\href{https://github.com/blairg23}{@blairg23}}. The rest may be in private repositories on Bitbucket \textbf{\href{https://bitbucket.com/blairg23}{blairg23}}.
\begin{enumerate}[]
	\item \large{Grad Projects}
		\small
		\begin{enumerate}[]
			\item \textbf{Bak-Tang-Wiesenfeld Model for Displaying Self-Organized Criticality}\\
				Also known as the Abelian Sandpile Model, this Python/Matplotlib application simulates sand being poured on a single point.
			\item \textbf{Earthquakes}\\
				A Python script to plot earthquakes that have occurred in the world, using the Matplotlib Basemap module.
			\item \textbf{Hoot, aka The Wolf Box}\\
				A hardware/software solution for broadcasting and recording sounds in adverse climates.
			\item \textbf{Particle Simulator}\\
				A particle physics simulator written in Python using the OpenGL libraries.
		\end{enumerate}
	\item \large{Personal Projects}
		\small
		\begin{enumerate}[]
			\item \textbf{bookmarks-manager}\\
				Bookmarks Tagr\textsuperscript{\textcopyright} is a full RESTful API for importing your Chrome bookmarks and creating a highly organized network graph of bookmarks and tags. Notable features include smart tagging, social sharing, up/down voting, and reporting bad links for removal.
			\item \textbf{BetterPassword}\\
				A short script to turn an easily remembered password into a large hashed password for better security in online applications.
			\item \textbf{create-api-wrappers}\\
				Reynold's RESTful Wrapper\textsuperscript{\textcopyright} is an application that creates API wrapper methods in Python from a list of API endpoints and their valid parameters.
			\item \textbf{delete-files}\\
				A short script to recursively remove all files within a given directory, given a regex match.
			\item \textbf{expense-analysis}\\
				Expensive\textsuperscript{\textcopyright} is an application that takes CSV files as input and builds a database of financial transactions to perform financial data analysis tasks, such as analyzing spending habits to build a budget.
			\item \textbf{files-in-folder}\\
				An application designed to perform an md5 hash-wise diff on files in two given directories. Outputs the contents of the folder (filenames and hash) and the diff as a CSV.
			\item \textbf{images-from-url}\\
				An application designed to scrape images off any given URL or REST API. On the last commit, it supported Imgur, Instagram, Tumblr, and any raw HTML website.
			\item \textbf{Nutflux}\\
				A suite of small applications centered around multimedia consumption, Nutflux\textsuperscript{\textcopyright} started as a Netflix clone for consuming your local multimedia collection. Now this suite contains multiple utilities for create a better multimedia experience.
				\begin{enumerate}[]
					\item \textbf{movie-decider}\\
						An application that takes your current multimedia collection and helps decide what you want to watch based on a series of mood questions.
					\item \textbf{movie-file-fixer}\\
						An application for formatting poorly formatted movie filenames, adding a movie poster from IMDb, and adding subtitles based on the md5 hash of the file. Recent commits started adding support for finding poor resolution files for replacement.
					\item \textbf{movie-tv-show-reminder}\\
						An application that reminders you when your favorite shows have new episodes or a new season.
					\item \textbf{movie-viewer}\\
						A Netflix clone that uses the Plex API to showcase your multimedia collection.
					\item \textbf{music-file-fixer}\\
						Like movie-file-fixer, but for music files.
				\end{enumerate}
			\item \textbf{rename-images-to-datetime}\\
				A short script to rename image files to a datetime format based on the datetime the image was produced. Can also format from one datetime format to another. Many cameras name their files like DSC\_0001.png, even if that file has already been created. This script's objective was to create unique files based on that unique datetime format.
			\item \textbf{TweetyPy}\\
				A Python Twitter client with a wrapper method for every Twitter REST API endpoint. Powered by \textbf{Reynold's RESTful Wrapper\textsuperscript{\textcopyright}}.
		\end{enumerate}
\end{enumerate}

\newpage
\noindent
\huge{Professional References}\\
\small
\begin{enumerate}[]
	\item \large \textbf{TOMIS, Inc.} \small
		\begin{enumerate}[]
			\item \textbf{Evan Tipton} - Founder, CEO - 404.217.1611
			\item \textbf{Michelle Jernigan} - Director of Marketing - 404.384.7318
			\item \textbf{Shane Cavaliere} - UI/UX Designer, Sr. Software Engineer - 406.544.8803
			\item \textbf{Aemil Estvold} - Optimizations / Integrations Engineer - 406.396.1265
			\item \textbf{Cole Carter} - Quality Assurance / Automations Engineer - 707.484.2228
		\end{enumerate}
	\item \large \textbf{dotmos, LLC.} \small
		\begin{enumerate}[]
			\item \textbf{Rod Austin} - CEO - 406.396.0673
			\item \textbf{Gary Greyling} - Sr. Software Engineer - +64.210.541.798 (NZ)
		\end{enumerate}
	\item \large \textbf{Upstream Research, Inc.} \small
		\begin{enumerate}[]
			\item \textbf{Alex Philp, PhD.} - Co-Founder, CSO - 406.370.2262
			\item \textbf{Jordan Larson} - Senior Economist - 406.830.8807
			\item \textbf{David Bechtold} - Senior Software Developer - 406.529.9606
		\end{enumerate}
	\item \large \textbf{Hanna-James Enterprises, LLC.} \small
		\begin{enumerate}[]
			\item \textbf{Misti and Dan James} - President/CEO and Vice President - 406.546.4602
			\item \textbf{Bradley Bahls} - Lead Project Manager, Senior Software Developer - 406.207.6351
		\end{enumerate}
	\item \large \textbf{University of Montana} \small
		\begin{enumerate}[]
			\item \textbf{Doug Raiford, PhD.} - Professor, Computer Science Department - 406.243.5605
			\item \textbf{Joel Henry, PhD, JD.} - Professor, Computer Science Department, Master's Defense Committee Chair - 406.243.2218
			\item \textbf{Jesse Johnson, PhD.} - Professor, Computer Science Department Chair - 406.243.2356
			\item \textbf{Yolanda Reimer, PhD.} - Professor, Computer Science Department, Master's Defense Committee Member - 406.243.4618
			\item \textbf{Johnathan Bardsley, PhD.} - Professor, Mathematics Department, Master's Defense Committee Member - 406.243.5328
		\end{enumerate}
\end{enumerate}
\end{document}